Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2024-09-06 whittaker.tex
Many changes required to fix the issues with \g versus \g^*.

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\Wh}{\mathrm{Wh}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
\begin{document}
\title{Whittaker Models for Real Groups}
\author{Jeffrey Adams \& Alexandre Afgoustidis}
\maketitle

@@

\subsubsection*{Nilpotent orbits} 
\label{s:nilpotentorbits}
Let $\N$ be the set of nilpotent elements of $\g$.

We need to pass to the dual Lie algebra $\g^*$. We follow  \cite[Section 2]{AVAV}.
Define $\N^*\subset \g^*$ to be the set of elements whose orbit is a cone.
We identify $\g$ and $\g^*$ using  a non-degenerate invariant bilinear form on $\g$. Given an element~$X$ in $\g$ we sometimes write $X^\ast$ for the corresponding element of~$\g^\ast$.

The identification $\g \simeq \g^\ast$ restricts to a bijection $\N\simeq \N^*$. Although this correspondence depends on the choice of form,
the induced bijection on the level of $G$-orbits is canonical.

We define $\O_p$ to be the \emph{principal nilpotent orbit} in $\N^*$: this is the unique orbit whose closure is  $\N^*$.

We may assume the chosen bilinear form on~$\g$ is $\theta$-invariant. In this case the identification between $\g=\mathfrak k+\s$ and $\g^*=\mathfrak k^*\oplus \s^*$ determines a $K$-equivariant  (but non-canonical) isomorphism between $\s$ and $\s^\ast$. This induces
a canonical bijection between $K$-orbits on $\s$ and on $\s^*$.

@@

A slightly different invariant is the associated variety of the annihilator. Let $I_\pi$ be the annihlator of $\pi$ in the universal enveloping algebra.
Let $\AVann(\pi)\subset\N^*\subset \g^*$ be the associated variety of $I_\pi$.
This is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.

@@

We write $\Wh(\pi)$ for the set of Whittaker data~$\w$ such that $\pi$ has a $\w$-Whittaker model.

@@

\begin{lemma}
  \label{l:large}
  The following conditions are equivalent.
  \begin{enumerate}
    \item $\pi$ is large;
\item $\AVann(\pi)=\N^*=\overline{\Op}$;
\item $\dim(\AVann(\pi))=N$;
  \item $\dim(\AV(\pi))=N/2$;
  \item $\GK(\pi)=N/2$;
    \item $\pi$ is generic.

\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

@@

\begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between\textup{:}
\begin{enumerate}
\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$\textup{;}
\item[(2)] The set of Whittaker data for $G(\R)$\textup{;}
\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$\textup{;}
\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$\textup{.}
\end{enumerate}
In particular if $\pi$ is a large discrete series representation then each of these three invariants of $\pi$ determines the other two. 
\end{theorem}

@@

As for~(2), it follows directly from the definition of the associated variety. This uses filtrations of the universal enveloping algebra of~$\g$ which are all invariant under $\Gad^{\theta_{\ad}}$: see for instance the Introduction of~\cite{vogan_bowdoin}. Inspecting the definitions in \emph{loc. cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a large discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(2). 
\qed

@@

\subsection{Whittaker data to real orbits ((2) $\leftrightarrow$ (4))}

First we describe the set of Whittaker data more explicitly.
Let $B$ be a Borel subgroup of $G$. Let $N$ be the nilradical of $B$, and $\overline N$ the opposite
nilpotent subgroup. Let $\n,\overline\n$ be the Lie algebras of $N,\overline N$.
If $B$ is defined over $\R$ we consider $N(\R),\n(\R), \overline\n(\R)$, etc.
For $X\in i\overline \n(\R)^*$ define a unitary character $\psi_X$ of $N(\R)$ by:
$$
\psi_X(e^Y)=e^{X(Y)}\quad(Y\in \n(\R)).
$$
The map $X\rightarrow \psi_X$ is an isomorphism between $i\overline\n(\R)^*$ and the unitary characters of $N(\R)$.
It is easy to see that $\psi_X$ is nondegenerate (i.e. satisfies condition~(ii) in the Introduction) if and only if $X\in i\g(\R)^*$ is a principal nilpotent element.
Therefore the pair $(B(\R),X)$ determines a Whittaker datum $\mathfrak{w}_{X}$: the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$. We do not keep track of~$B$ in the notation because~$\mathfrak{w}_X$ doesn't depend on this choice: see~\cite[Section~3.1]{adams_kaletha}.

The correspondence $\mathfrak{w}_{X} \leftrightarrow G(\R)\cdot X$ defines a bijection between Whittaker data and
$(\Op(\R)\cap i\g(\R)^*)/G(\R)$. The main result of \cite{matumoto} (Theorem A) says:

\begin{lemma}\label{lem:matumoto}
The bijection (2)$\leftrightarrow$(4) takes the Whittaker datum $\mathfrak{w}_{X}$ to
the principal orbit $G(\R)\cdot X$. 
 \end{lemma}

\subsection{Large discrete series to $K$-orbits ((1) $\leftrightarrow$ (3))}

@@

\begin{lemma}[(1)$\leftrightarrow$(3)]\label{l:pi_to_av}
Suppose $\pi$ is a large discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
Set

@@

Then $F_\pi\in\s$ is a regular nilpotent element. Let $F_\pi^\ast\in \N^*$ be the corresponding element (cf. Section \ref{s:nilpotentorbits}).
Then 
$$
\AV(\pi)=\overline{K\cdot F_\pi^\ast}.
$$
\end{lemma}
See
\cite[Propositions A.7 and A.9]{AV1}.

\subsection{Large discrete series to real orbits ((1) $\leftrightarrow$ (4))}\label{sec:asymp_cone}

@@

For this see \cite{HarrisHeOlafsson}; in the special case considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed

@@

\subsection{Large discrete series to Whittaker data ((1) $\leftrightarrow$ (2))}

We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between large discrete series and Whittaker data using  {\it Kostant sections}. Let~$X$ be a regular nilpotent element of~$\g$, and choose  $H, Y \in \g$ such that $(X,H,Y)$ is an  $\SL(2)$-triple. The Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$. This depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.

Using the given identification $\g \simeq \g^\ast$, if $X \in i\g(\R)^\ast$ is a regular nilpotent element, then it makes sense to talk about the Kostant section $\Kostant{X} \subset \g^\ast$. The notation hides the dependence on a choice of $\mathrm{SL}(2)$-triple.

\begin{proposition}[\cite{adams_kaletha}]\label{JeffTasho_criterion}
Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)^*$ be a regular nilpotent element such that $\w = \w_X$. 
Then $\pi$ is $\w$-generic if and only if $\Kostant{X}$ meets $\mathcal{O}_\pi$. 
\end{proposition}

@@

\subsection{Connection between ((3) $\leftrightarrow$ (4)) and the Kostant--Sekiguchi correspondence }

It is well known that a natural bijection between nilpotent $K$-orbits and nilpotent $G(\R)$-orbits can be defined in more elementary terms. This is the Kostant--Sekiguchi correspondence~\cite{sekiguchi}. Furthermore, it is a deep theorem of Schmid and Vilonen (the main result of~\cite{SV1}) that the wavefront set and the associated variety are exchanged by this correspondence. (As a historical aside, the Kostant--Sekiguchi correspondence was discovered on the basis that the correspondence $\AV(\pi) \leftrightarrow \WF(\pi)$ might be expressed in elementary terms.)

Therefore, a particular case of Schmid and Vilonen's theorem says: 
\begin{proposition} \label{Sekiguchi_result} The bijection (3)--(4) is induced by the Kostant--Sekiguchi correspondence.
\end{proposition} 
We shall do two things here. First, we will quote a result of \cite{AVAV} which makes this case of the Kostant--Sekiguchi correspondence completely explicit. Second, we shall give a new and elementary proof of Proposition~\ref{Sekiguchi_result}: this avoids the use of Schmid and Vilonen's difficult results, and instead uses the results above (in particular Proposition~\ref{JeffTasho_criterion}) as the main ingredients.

Suppose $\xi_\R\in \Op\cap i\g(\R)^\ast$, and write $\xi_\R = E_\R^\ast$ where $E_\R$ is a principal nilpotent element. We may choose $H_\R, E_\R \in \g$ such that $(H_\R,E_\R,F_\R)$ is an $\mathrm{SL}(2)$-triple and  $E_\R$  contained in $i\g(\R)$,
which implies $H_\R\in \g(\R)$. 
After conjugating by~$G(\R)$ we may further assume $\theta(E_\R)=-F_\R$. Set 
\[   E_\theta=\frac12(E_\R-F_\R+H_\R)\quad
F_\theta=\frac12(-E_\R+F_\R+H_\R)
\]
Then $E^\ast_\theta,F^\ast_\theta\in \Op\cap \s$, and the Sekiguchi correspondence takes the $G(\R)$-orbit of~$E^*_\R$ to the $K$-orbit of $E_\theta^\ast$. 
Equivalently, it takes the $G(\R)$-orbit of $F^*_\R$ to the $K$-orbits of $F_\theta^\ast$.

Computing the map in the other direction goes as follows.
Suppose $\xi_\theta \in \Op\cap \s^\ast$, and write $\xi_\theta=E_\theta^\ast$. Choose $F_\theta, H_\theta \in \g$ such that $(E_\theta, H_\theta, F_\theta)$ is an $SL(2)$-triple with $F_\theta \in \s$,  which implies $H_\theta\in\k$. After conjugating by $K$ we may further assume $\sigma(E_\theta)=F_\theta$.
Define 
\begin{equation}\label{def_F_R}
E_\R=\frac12(E_\theta-F_\theta-H_\theta)\quad
F_\R=\frac12(-E_\theta+F_\theta-H_\theta).
\end{equation}
Then the Sekiguchi correspondence takes the $K$-orbit of $E^*_\theta$ (resp. $F^*_\theta$) to the $G(\R)$-orbit of $E_\R^\ast$ (resp. $F_\R^\ast$).

Let us fix a generic discrete representation~$\pi$, a representative~$\lambda \in \t^\ast$ for the Harish-Chandra parameter, and we write~$H_\lambda$ for the element of~$\t$ such that $H_\lambda^\ast=\lambda$. In the rest of this section we use the identification $\g \simeq \g^\ast$ implicitly, and do not distinguish between adjoint and coadjoint orbits, Weyl chambers in $\t$ and $\t^\ast$, etc.

Consider the principal nilpotent element~$F_\pi$ defined in~\eqref{e:Fpi}. Let us use this as~$F_\theta$ in the previous subsection: define $E_\theta = \sum_{\alpha \in S(\lambda)}X_\alpha$ and $H_\theta  = [E_\theta, F_\theta]$; then $E_\theta \in \s$ and $(E_\theta, H_\theta, F_\theta)$ is an $\mathrm{SL}(2)$-triple. Define another $\mathrm{SL}(2)$-triple $(E_\R, F_\R, H_\R)$ by
\[ \begin{aligned}
  F_\R&=\frac12(-E_\theta+F_\theta-H_\theta)\\
  E_\R&=\frac12(E_\theta-F_\theta-H_\theta)\\
  H_\R&=E_\theta+F_\theta.
\end{aligned}\]

We know that  $\AV(\pi)=K \cdot F^*_\pi$, so the image of $\AV(\pi)$ by the Sekiguchi correspondence is 
 $G(\R)\cdot F_\R$. We want to check that this is equal to $\WF(\pi)$.

By Lemma~\ref{lem:matumoto} it is enough to check that $\pi$ is $\w$-generic for the Whittaker datum $\w$ corresponding to~$F_\R$. By Proposition~\ref{JeffTasho_criterion} this is the case if and only if the Kostant section $\Kostant{F_\R}$ meets $\mathcal{O}_\pi$.

Now, we know that $\Kostant{F_\R}=F_\R+\mathrm{Cent}_\g(E_\R)$ contains $F_\R+E_\R = -H_\theta$. However, $H_\theta$ does not have to be on~$\mathcal{O}_\pi$: in general $\mathcal{O}_\pi=G(\R) \cdot H_\lambda$ and $G(\R) \cdot (-H_\theta)$ are disjoint orbits. 
Nevertheless $H_{\lambda}$ and $-H_\theta=[F_\theta, E_\theta] = \sum_{\alpha \in S(\lambda)} [X_{-\alpha,} X_\alpha]$ are in the same Weyl chamber.  Therefore the result follows from:

\begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
If $H$ and $H'$ are  points of~$\mathcal{C}$ and $\mathcal{O}, \mathcal{O}'$ are the   $G(\R)$-orbits of $H$ and $H'$, then $\AC(\mathcal{O})=\AC(\mathcal{O}')$.
\end{proposition}

We shall prove this in the rest of this section, based on the following lemma.

\begin{lemma}\label{lem:Kost_and_AC} Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element. Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$.

Consequently each of the three invariants $\Wh(\pi),\AV(\pi)$ and $\WF(\pi)$ remain constant if $\pi=\pi_{\lambda, \zeta}$ is a large discrete series representation, and $\lambda$ varies in a fixed large Weyl chamber.
\end{lemma}
\begin{proof} 
If $X\in \AC(\mathcal O)$ then $\Kostant{X}$ meets $\mathcal O$ by \cite[Lemma 3.2.3]{adams_kaletha}.

Suppose $\Kostant{X}$ meets $\mathcal O$.
This means there is an $SL(2)$-triple $(X,H,Y)$, and an element $Z\in \Cent_\g(Y)$ such that $W=X+Z \in \O$. 
By \cite{Kostant59}, the centralizer  $\mathrm{Cent}_{\g}(Y)$ is abelian; furthermore there exists a Cartan subalgebra $\mathfrak{h} \subset \g$, and a positive system $\Delta$ for the roots of $\mathfrak{h}$ in $\g$, such that $E$ is contained in the sum of $\Delta$-positive root spaces, while $\mathrm{Cent}_{\g}(F)$ is contained in the sum of $\Delta$-negative roots.  Therefore, if we set $h(t) = \exp(tH)$ for $t \in \R_+$, then 
\[\begin{cases} \mathrm{Ad}(h(t)) \cdot F \longrightarrow 0 & \text{as $t \to +\infty$, while} \\
 \mathrm{Ad}(h(t)) \cdot E = f(t) E & \text{ with $f(t) >0$ and $f(t)\to +\infty$ as $t \to \infty$.}\end{cases}\]
Set $Y(t) = \mathrm{Ad}(h(t)) Y$; then $f(t) \left[ E + Y(t) \right] = \mathrm{Ad}(h(t)) W$ lies on the orbit~$\mathcal{O}$. Thus there exists a continuous path in $\R^+ \cdot \mathcal{O}$ with $E=X$ as a limit point; by definition this means $X \in \AC(\mathcal{O})$.%By the representation theory of $SL(2)$ we know that $Z=\sum_{j=0}^n Z_j$ with $[H,Z_j]=-jZ_j$. 
%Then 
%$$
%\Ad(e^{tH})(X+Z)=e^{2t}(X) + \sum_j e^{-tj}Z_j
%$$
%Taking the limit as $t\rightarrow 0$ gives $\Ad(e^{tH})(X+Z)\rightarrow e^{2t}X$. Therefore
%$$
%\lim_{t\rightarrow 0}e^{-2t}\Ad(e^{tH})(X+Z)=X
%$$ which implies the result.
\end{proof}

@@

\medskip

The connection between Lemma~\ref{lem:Kost_and_AC} and Proposition~\ref{prop:AC_chamber} is that Lemma~\ref{lem:Kost_and_AC}  implies the  following observation on the behavior of the asymptotic cone of regular semisimple orbits:

@@

\begin{proof}
Let $F$ be an element of~$\Omega$, and let $\mathcal{O}$  be a regular semisimple orbit such that $\AC(\mathcal{O})$ contains~$\Omega$.
Then $\Kostant{F}$ meets $\mathcal{O}$ by  Lemma~\ref{lem:Kost_and_AC}. 
Fix $X$ in $\mathcal{O} \cap \Kostant{F}$.
We have $X =F+Y$ where $Y$ belongs to the centralizer $\mathrm{Cent}_\g(F)$.
Since this centralizer is transverse to the $G(\R)$-orbits and has dimension $\dim(\g(\R))-\dim(\t(\R))$,
there exists an open neighborhood of~$X$ consisting of (regular semisimple) orbits  which meet $\Kostant{F}$.
Using Lemma~\ref{lem:Kost_and_AC} again, we see that all those orbits $\mathcal{O}'$ satisfy $F \in \AC(\mathcal{O}')$,
which implies that $\Omega = G(\R) \cdot F$ is contained in $\AC(\mathcal{O}')$.
This proves that $\mathcal{E}_\Omega$ contains an open neighborhood of any of its points, hence is open.   \end{proof}

Let us prove Proposition~\ref{prop:AC_chamber}. Given an element $H$ of $\mathcal{C}$, we shall write $\mathcal{O}_H$ for the $G(\R)$-orbit of~$H$. For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.

@@

Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some large discrete series representation. Since the Harish-Chandra parameters for discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$. Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one large discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$. By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a large discrete series.

>>>>

\renewcommand{\t}{\mathfrak t}
\newcommand{\su}{\mathfrak s\mathfrak u}
\newcommand{\g}{\mathfrak g}
\newcommand{\gder}{\mathfrak g_{\mathrm{der}}}
\newcommand\inv{^{-1}}
\newcommand\wh{\widehat}
\newcommand{\GL}{\text{GL}}
\newcommand{\SL}{\text{SL}}
\newcommand{\SO}{\text{SO}}
\newcommand{\SU}{\text{SU}}
\newcommand{\Spin}{\text{Spin}}
\newcommand{\chGGamma}{\phantom{a}^\vee G^\Gamma}
\newcommand{\GGamma}{G^\Gamma}
\newcommand{\s}{\mathfrak s}
\newcommand{\w}{\mathfrak w}
\newcommand{\AV}{\mathrm{AV}}
\newcommand{\KS}{\mathcal{KS}}
\newcommand{\Wh}{\mathrm{Wh}}
\newcommand{\WF}{\mathrm{WF}}
\newcommand{\AC}{\mathrm{AC}}
\newcommand{\AVann}{\mathrm{AV}_{\mathrm{ann}}}
\newcommand{\GK}{\mathrm{GK}}
\newcommand{\Op}{\O_p}
\newcommand{\Kostant}[1]{\mathcal{K}(#1)}
\newcommand{\ECom}{\mathcal{E}^{\mathcal{C}}_\Omega}
\begin{document}
\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams \& Alexandre Afgoustidis}
\maketitle

@@

\subsubsection*{Nilpotent orbits in $\g^*$} 
\label{s:dual}
Let $\N$ be the set of nilpotent elements of $\g$.

We need to pass to the dual Lie algebra $\g^*$.
We say an element of $\g^*$ is nilpotent if its $G$-orbit is a (weak) cone, i.e. closed under multiplication by $\C^*$,
and \emph{regular} if $\dim_{\Cent(G)}(X)=\mathrm{rank}(G)$.  
The principal nilpotent orbit $\O_p\in \g^*$ is the set of regular nilpotent elements.

The statements of the main results do not require the choice of an isomorphism $\g\simeq \g^*$.
In several places we do need to make such a choice;
with the exception of (?) this choice will not matter.

So we fix a non-degenerate, $G(\R)$-invariant bilinear form $\kappa$ on $\g(\R)$. This is equivalent to having a non-degenerate, $G(\C)$ and Galois invariant
bilinear form on $\g$. The restriction of the form each simple factor
is unique up to a non-zero constant. For example we can use the Killing form on $\gder$, extended arbitrarily by a non-degenerate form on the center.

Given $\kappa$ we define
$\psi_\kappa: \g\rightarrow \g^*$ as usual:
$$
\psi_\kappa(X)(Y)=\kappa(X,Y)\quad (X,Y\in\g).
$$

Using $\psi_\kappa$ we transfer the asymptotic cone, Kostant section, and Kostant Sekiguchi corresondence to $\g^*$. In each case these constructions are independent of the
choice of $\kappa$. See (?).

In Section \ref{s:AV} we need to be more precise: we choose  $\kappa$ to be the Killing form. (More generally, we could take any non-degenerate
invariant form which is negative definite on the Lie algebra of a maximal compact subgroup.)

@@

A related invariant is the associated variety of the annihilator $I_\pi$ of $\pi$ in the universal enveloping algebra, 
denoted $\AVann(\pi)$.
This is a subset of $\N^*\subset\g^*$, and is the closure of a single complex nilpotent orbit: see \cite[Section 1, Theorem 4.7]{vogan_bowdoin}.

@@

We write $\Wh(\pi)$ for the set of Whittaker data~$\w$ such that $\pi$ has a $\w$-Whittaker model.
If $\pi$ has a unique Whittaker datum $\w$ we write $\Wh(\pi)=\w$.

@@

\begin{lemma}
  \label{l:large}
  The following conditions are equivalent.
  \begin{enumerate}
  \item $\pi$ is large;
        \item $\pi$ is generic.
\item $\AVann(\pi)=\N^*=\overline{\Op}$;
\item $\dim(\AVann(\pi))=N$;
  \item $\dim(\AV(\pi))=N/2$;
  \item $\GK(\pi)=N/2$;
\end{enumerate}
\end{lemma}
See \cite{vogan_bowdoin}, in particular Corollary 4.7 and Theorem 8.4.

From now on we use the terms {\it large} and {\it generic} interchangeably.

@@

\begin{theorem} \label{th:main} Suppose~$\Pi$ is an $L$-packet of discrete series for~$G(\R)$. 
The maps $\pi \mapsto \Wh(\pi)$, $\pi \mapsto \AV(\pi)$ and $\pi\mapsto \WF(\pi)$ induce bijections between\textup{:}
\begin{enumerate}
\item[(1)] The set~$\Pi_{\mathrm{gen}}$ of generic discrete series representations in~$\Pi$\textup{;}
\item[(2)] The set of Whittaker data for $G(\R)$\textup{;}
\item[(3)] The set of~$K$-orbits on $\mathcal{O}_p \cap \s^*$\textup{;}
\item[(4)] The set of~$G(\R)$-orbits on $\mathcal{O}_p \cap  i \g(\R)^*$\textup{.}
\end{enumerate}
In particular if $\pi$ is a generic discrete series representation then each of these three invariants of $\pi$ determines the other two. 
\end{theorem}

@@

As for~(2), it follows directly from the definition of the associated variety. This uses filtrations of the universal enveloping algebra of~$\g$ which are all invariant under $\Gad^{\theta_{\ad}}$: see for instance the Introduction of~\cite{vogan_bowdoin}. Inspecting the definitions in \emph{loc. cit.} it becomes clear that the map $\pi \mapsto \AV(\pi)$, taking a generic discrete series $(\g,K)$-module  (or rather its equivalence class) to its associated variety, is equivariant under~$Q_{\theta}(G)$, proving~(2). 
\qed

@@

\subsection{Associated Variety of generic discrete series}
\label{s:AV}

@@

In this section only we need to  choose a particular an isomorphism $\gder\simeq \gder^*$.
For this we let $\kappa$ be the killing form, and define $\psi:\gder\rightarrow \gder^*$ by
$$
\psi(X)(Y)=\kappa(X,Y)\quad (X,Y\in \gder).
$$

\begin{lemma}
\label{l:pi_to_av}
  \label{l:AV}
Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda\in\t^*$.
Set

@@

Then $F_\pi\in\s$ is a regular nilpotent element.
Then 
$$
\AV(\pi)=K\cdot \psi(F_\pi).
$$
\end{lemma}
See
\cite[Propositions A.7 and A.9]{AV1}.

\begin{remarkplain}
Note that $\psi_{-\kappa}(F_\pi)=-\psi_{\kappa}(F_\pi)$, and these are not necessarily $K$-conjugate.
  This is the reason we need to use (a positive multiple of) the Killing form for this formula.
\end{remarkplain}

\subsection{Wave front set of generic discrete series}\label{sec:asymp_cone}

@@

For this see \cite{HarrisHeOlafsson}; in the special casea considered here, the result is due to Rossmann and can be extracted from \cite{RossmannPicard}, Theorems B and C. \qed

@@

\subsection{Whittaker data of generic discrete series}

The following discussion is taken directly from \cite[Section~3.1]{adams_kaletha}.

Suppose $X\in i\g(\R)^*\subset \g^*$ is a regular nilpotent element (see Section \ref{s:dual}).
Let $\overline{\mathfrak b}(\R)$ be the kernel of $X$. 
The corresponding Borel subgroup $B$ is defined over $\R$.
Choose an $\R$-Cartan subgroup $T$ of
$\overline B$, and let $B$ be the corresponding opposite Borel
subgroup (characterized by $B\cap \overline B=T$). 
Then $X$ defines a unitary
character of the nilradical  $N(\R)$  of $B(\R)$ by
\[ 
\psi_X(\exp Y)=e^{X(Y)}\quad (Y\in\n(\R)).
\] 
We define $\w_X$ to be the $G(\R)$-conjugacy class of $(B(\R),\psi_X)$; as the notation indicates this is independent 
of the choice of $T$.

The correspondence $\mathfrak{w}_{X} \leftrightarrow G(\R)\cdot X$ defines a bijection between Whittaker data and
$(\Op(\R)\cap i\g(\R)^*)/G(\R)$.

We recall a recent result of the first author and Tasho Kaletha, which spells out the connection between generic discrete series and Whittaker data using  {\it Kostant sections}. Let~$X$ be a regular nilpotent element of~$\g$, and choose  $H, Y \in \g$ such that $(X,H,Y)$ is an  $\SL(2)$-triple. The Kostant section~$\Kostant{X}$ is the affine subspace $X + \mathrm{Cent}_{\g}(Y)$ of~$\g$. This depends on the choice of $\SL(2)$-triple, but if $X \in \g(\R)$, then the $G(\R)$-conjugacy class of~$\Kostant{X}$ depends only on the $G(\R)$-conjugacy class of~$X$.

We define the Kostant section in $\g^*$ using an identification $\g\simeq \g^*$ as discussed in Section \ref{s:dual}. That is we fix an equivariant isomorphism $\psi$, and define
$$
\K(X)=\psi(\K(\psi\inv(X))\quad (X\in \g^*)
$$
Since $\psi$ is unique on each simple factor up to non-zero scalar, it is easy to see this definition is independent of the choice of $\psi$. See \cite[Section 3.2]{adams_kaletha}.

\begin{proposition}[\phantom{}{\cite[Proposition 3.3.3]{adams_kaletha}}]\label{JeffTasho_criterion}
  \label{p:Kostant}
Suppose $\pi$ is a generic discrete series representation of~$G(\R)$. Suppose~$\pi$ be a Whittaker datum for~$G(\R)$, and let~$X \in i\g(\R)^*$ be a regular nilpotent element such that $\w = \w_X$. 
Then $\pi$ is $\w$-generic if and only if $\Kostant{X}$ meets $\mathcal{O}_\pi$. 
\end{proposition}

@@

\begin{lemma}[\phantom{}{\cite[Lemma 3.3.4]{adams_kaletha}}]
\label{lem:Kost_and_AC}
Let $\mathcal{O}$ be a regular semisimple orbit and  let $X$ be a regular nilpotent element. Then $\Kostant{X}$ meets~$\mathcal{O}$ if and only if $X$ is in the asymptotic cone~$\AC(\mathcal{O})$. 
\end{lemma}

@@

The Proposition, Lemma and Lemma \ref{lem:WF_and_AC} give the following result,
which is a special case of the main result of \cite{matumoto} (Theorem A).

\begin{corollary}\label{cor:matumoto}
Suppose $\pi$ is a generic discrete series representation. Then
$$
\Wh(\pi)=\w_X\Leftrightarrow \WF(\pi)=G(\R)\cdot X.
$$
\end{corollary}

\subsection{Geometry of Kostant sections and asymptotic cones}

By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the Weyl chamber of its Harish-Chandra parameter. 
The same holds for the wave front set and Whittaker data by Theorem \ref{th:main}. This can also be proved directly 
using some geometric facts.

Write $\O_H$ for the $G(\R)$-orbit of $H$.

\begin{proposition}\label{prop:AC_chamber} Let $\mathcal{C} \subset \t$ be a large open Weyl chamber.
  If $H,H'\in\mathcal{C}$  then $\AC(\mathcal{O}_H)=\AC(\mathcal{O}_{H'})$.

  Suppose $X$ is a regular nilpotent element. Then $\K(X)\cap \O_H\ne \emptyset$ if and only if $\K(X)\cap \O_{H'}\ne\emptyset$.
\end{proposition}

Before giving the proof we need a Lemma.

@@

\begin{proof}

Let $F$ be an element of~$\Omega$, and let $\mathcal{O}$  be a regular semisimple orbit such that $\AC(\mathcal{O})$ contains~$\Omega$.
Then $\Kostant{F}$ meets $\mathcal{O}$ by  Lemma~\ref{lem:Kost_and_AC}. 
Fix $X$ in $\mathcal{O} \cap \Kostant{F}$.
We have $X =F+Y$ where $Y$ belongs to the centralizer $\mathrm{Cent}_\g(F)$.
Since this centralizer is transverse to the $G(\R)$-orbits and has dimension $\dim(\g(\R))-\dim(\t(\R))$,
there exists an open neighborhood of~$X$ consisting of (regular semisimple) orbits  which meet $\Kostant{F}$.
Using Lemma~\ref{lem:Kost_and_AC} again, we see that all those orbits $\mathcal{O}'$ satisfy $F \in \AC(\mathcal{O}')$,
which implies that $\Omega = G(\R) \cdot F$ is contained in $\AC(\mathcal{O}')$.
This proves that $\mathcal{E}_\Omega$ contains an open neighborhood of any of its points, hence is open.   \end{proof}

\begin{proof}[proof of the  Proposition]
For any regular nilpotent orbit~$\Omega$ let $\ECom$  denote the set of $H \in \mathcal{C}$ such that $\AC(\mathcal{O}_H)$ contains $\Omega$; by Lemma~\ref{lem:AC_containment}  we know that   $\ECom$ is an open subset of~$\mathcal{C}$.

@@

Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some generic discrete series representation. Since the Harish-Chandra parameters for discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$. Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$. By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.

We conclude that if $\Omega \neq \Omega'$, then $\mathcal{S}_\Omega$ and $\mathcal{S}_\Omega$ are disjoint, and therefore $\ECom$ and $\mathcal{E}^{\mathcal{C}}_{\Omega'}$ are disjoint open subsets of~$\mathcal{C}$. Since $\mathcal{C}$ is connected and equal to the union of all subsets $\mathcal{E}^{\mathcal{C}}_{\Omega}$, the chamber $\mathcal{C}$ must be equal to a single $\ECom$.

The second assertion is an immediate consequence of the first and Lemma \ref{lem:Kost_and_AC}

\end{proof}

\begin{corollary}
\label{c:same}
Suppose $\pi$ is a generic discrete series representation with Harish-Chandra parameter $\lambda$.
Then $\AV(\pi)$, $\WF(\pi)$ and $\Wh(\pi)$ only depend on the Weyl chamber of $\lambda$.
\end{corollary}
